Czech parliament meeting recordings as ASR training data

### 2020-04-24 2020-tsd-brno-svolocz/svolocz.tex
ASR results and proof reading for svolocz

Training data for speech recognition is always a demanded commodity, especially
if it is free. There are for sure already some free Czech corpora fit for speech
recognition training:
\begin{itemize}
\item{
    Vystadial\cite{vystadialarticle} with its 77 hours of VoIP
    calls\cite{vystadialdata}, 
}
\item{
    The Prague Database of Spoken Czech\cite{pdtscarticle} with its 122 hours
    of richly annotated spontaneous dialogues\cite{pdtscdata},
}
\item{
    The Czech Senior COMPANION Expressive Speech Corpus with its 5 hours
    of professionally spoken utterances by a single speaker\cite{companiondata},
}
\item{
    Otázky Václava Moravce: 35 hours of transcribed recordings of the
    Czech TV talk show\cite{ovmdata},
}
\item{
    STAZKA, a set of speech recording from vehicles with its 35 hours of
    background noise and utterances\cite{stazkadata},
}
\item{
    Spoken Corpus of Karel Makoň\cite{kruuza2012making} with its 70 hours of
    manually transcribed spontaneous speech by a single speaker\cite{makondata},
}
\item{and possibly others that I am not aware of.}
\end{itemize}

The Czech parliament meeting recordings represent a publicly available dataset
of high-quality audio recordings of contemporary Czech in consistent low-noise
audio quality worth almost 4000 hours of downloadable material, about 2800 hours
with the overlaps subtracted. Extracting
training data for speech recognition systems would provide a corpus at least
one order greater in length than those so far publicly available.

@@

Systems for aligning long audio segments to their transcripts already exist,
like that of Moreno et al. 1998\cite{moreno1998recursive} or Hazen
2006\cite{hazen2006automatic}. They are both based on an already existing
automatically acquired transcript. I use this technique as well, though much
simplified.

@@

To create a usable dataset for training a speech-to-text system, it is not
necessary to perfectly align the whole transcript. It is fine to just select the
reliable segments.

@@

To ensure precise transcript, it is good to have the samples padded by some
silence, since the alignment may be a bit imprecise. The need to split at longer
pauses goes against the need to split at consistent, none-too-great lengths.

The problem of selecting the optimal set of silences so that the longest ones
are kept and split the recording in chunks of set length boundaries looks like
one for dynamic programming but a simpler approach is also possible: Start with a set of
all silences predicted by the forced alignment. Iterate over the silences
shortest-first and remove it if it doesn't break the constraints.

I have experimentally set the length boundaries to 12 - 30 seconds. The maximum
length could be decreased at the cost of more frequent splits in the middle of a
word.

@@

Minimum reliability of border tokens is considered to minimize the danger of
shifted alignment boundaries. Mean reliability is considered because it is OK for some
words to have reliability zero: there are enough errors in the prediction,
that's why we use the manual transcript after all. But if too many tokens have
too low reliability, then it is a sign of a suspicious segment. The number of
words has a minimum because with only a few words, the probability of
misalignment with good score is much greater than when there are enough words.

@@

All the constants and criteria are to be considered a baseline solution. They
all could be tweaked much more rigorously and solved much more soundly. However,
this simple solution readily yields a high-quality training dataset of 1058
hours. Of the total 539,057 segments, 142,530 (26\%) have been accepted to the
training dataset. Of the total 396,527 discarded segments, 350,258 (88\%) were
discarded because of the criterion of unreliable start or end.

@@

I have trained a standard DeepSpeech\cite{hannun2014deep} model with training :
dev : test ratio of 48 : 1 : 1; batch size 50; learning rate 0.0001. The
training took TODO epochs and the final WER on testing data from the corpus
itself was TODO.

@@

I have presented a new corpus of spoken Czech suitable for training speech
recognition systems based on data in the public domain. The corpus size exceed
by an order the size of other freely available such corpora.

Source code for scraping and building the corpus is in public domain and
available on \texttt{GitHub.com/Sixtease/cz-parliament-speech-corpus}.

>>>>

Training data for speech recognition is always a demanded commodity, especially
if it is free. There are for sure already some free Czech corpora fit for speech
recognition training:
\begin{itemize}
\item{
    Vystadial\cite{vystadialarticle} with its 77 hours of VoIP
    calls\cite{vystadialdata}, 
}
\item{
    The Prague Database of Spoken Czech\cite{pdtscarticle} with its 122 hours
    of richly annotated spontaneous dialogues\cite{pdtscdata},
}
\item{
    The Czech Senior COMPANION Expressive Speech Corpus with its 5 hours
    of professionally spoken utterances by a single speaker\cite{companiondata},
}
\item{
    Otázky Václava Moravce: 35 hours of transcribed recordings of the
    Czech TV talk show\cite{ovmdata},
}
\item{
    STAZKA, a set of speech recording from vehicles with its 35 hours of
    background noise and utterances\cite{stazkadata},
}
\item{
    Spoken Corpus of Karel Makoň\cite{kruuza2012making} with its 100 hours of
    manually transcribed spontaneous speech by a single speaker\cite{makondata},
}
\item{and possibly others that I am not aware of.}
\end{itemize}

The Czech parliament meeting recordings represent a publicly available dataset
of high-quality audio recordings of contemporary Czech in consistent low-noise
audio quality worth almost 4000 hours of downloadable material, about 2800 hours
after subtraction of the overlaps. Extracting
training data for speech recognition systems would provide a corpus at least
one order greater in length than those so far publicly available.

@@

Systems for aligning long audio segments to their transcripts already exist,
like that of Moreno et al.\cite{moreno1998recursive} or
Hazen\cite{hazen2006automatic}. They are both based on an already existing
automatically acquired transcript. I use this technique as well, though 
simplified and adapted to the task.

@@

To create a usable dataset for training a speech-to-text system, it is not
necessary to perfectly align the whole transcript. On the contrary, it is
desirable to align what is reliably precise and discard the rest.

@@

To ensure precise transcript, it is good to have the samples padded by some
silence, since the alignment obtained from the initial ASR may be a bit
imprecise. We thus want to split at pauses, the longer the better, up to a
certain limit (about 1 second). The need to split at longer
pauses goes against the need to split at consistent, none-too-great lengths.

So the problem is to select an optimal set of silences so that the longest ones
are used and so that they split the recording into chunks of length in a given
range. This looks like a problem for dynamic programming but a simpler approach
is also possible: Start with a set of all silences predicted by the forced
alignment.  Iterate over the silences shortest-first and remove each if it
doesn't break the constraints.

I have experimentally set the length boundaries to 12 - 30 seconds. The maximum
length could be decreased at the cost of available pauses to choose from, which
would lead to more frequent splits in the middle of a word.

@@

Minimum reliability of border tokens is considered to minimize the danger of
shifted alignment boundaries. Mean reliability is considered because it is OK
for some words to have very low reliability: there are enough errors in the
prediction, that's why we use the manual transcript after all. But if too many
tokens have too low reliability, then it is a sign of a suspicious segment. The
number of words has a minimum because with only a few words, the probability of
misalignment with good score is much greater than when there are enough words.

@@

All the constants and criteria are to be considered a baseline solution. They
all could be tweaked much more rigorously and solved much more soundly. However,
this simple solution readily yields a high-quality training dataset of 1058
hours. Of the total 539,057 segments, 142,530 (26\%) have been accepted to the
training dataset. Of the total 396,527 discarded segments, 350,258 (88\%) were
discarded because of the criterion of unreliable start or end. It should be
noted however, that the start / end reliability criterion is applied first, so
it catches segments that would be discarded for other reasons also.

@@

I have trained a standard DeepSpeech\cite{hannun2014deep} model on the 1058
hours with training :
development : test ratio of 48 : 1 : 1; batch size 50; learning rate 0.0001; dropout
rate 0.2. The training took 12 epochs to reach optimal dev fit and the final
word error rate on testing data from the corpus itself is 8.40\%.

The language model used was a pentagram model with pruned singleton trigrams,
tetragrams and pentagrams. The bulk of scraped transcriptions, including those
with no downloadable corresponding audio, was used as training data for the
language model.

@@

I have presented a new corpus of spoken Czech suitable for training speech
recognition systems based on data in the public domain. The corpus size exceed
by an order the size of other freely available such corpora. A speech
recognition system with competitive performance was made to show the fitness
of the dataset to the purpose.

Source code for scraping and building the corpus is in the public domain and
available on \texttt{GitHub.com/Sixtease/cz-parliament-speech-corpus}.
